Eco-evolutionary dynamics of finite populations from first principles

### 2023-03-26 ind_files/02_math_background.tex
Correct minor typo

That is to say, it is obtained by dividing our time interal into slices of the form $[t_i,t_{i+1}]$, computing the `area of the rectangle' formed with $W_{t_{i+1}}-W_{t_i}$ and $G(t_i,X_{t_i})$ as sides, and then taking the limit\footnote{If you know a little bit of mathematics, it bears noting that this limit is in $L^2(\mathbb{P})$, whereas the corresponding limit in the usual Riemann-Stieltjes integral is evaluated pointwise. If you don't know what this sentence means, just ignore it for the purposes of this thesis :)} of finer and finer slices of time. This should look similar to the classic Riemann integral, with the uniform width $t_{i+1}-t_i$ of the Riemann integral replaced by a random width $W_{t_{i+1}}-W_{t_i}$ corresponding to the (random) displacement of a Brownian particle during the uniform time interval $[t_i,t_{i+1}]$.\\

>>>>

That is to say, it is obtained by dividing our time interval into slices of the form $[t_i,t_{i+1}]$, computing the `area of the rectangle' formed with $W_{t_{i+1}}-W_{t_i}$ and $G(t_i,X_{t_i})$ as sides, and then taking the limit\footnote{If you know a little bit of mathematics, it bears noting that this limit is in $L^2(\mathbb{P})$, whereas the corresponding limit in the usual Riemann-Stieltjes integral is evaluated pointwise. If you don't know what this sentence means, just ignore it for the purposes of this thesis :)} of finer and finer slices of time. This should look similar to the classic Riemann integral, with the uniform width $t_{i+1}-t_i$ of the Riemann integral replaced by a random width $W_{t_{i+1}}-W_{t_i}$ corresponding to the (random) displacement of a Brownian particle during the uniform time interval $[t_i,t_{i+1}]$.\\
